Gsmodutils: A python based framework for test-driven genome scale metabolic model development

### 2018-09-27 article/article.tex
typo

\section{Related work}
\textbf{Memote:} \cite{lieven2017memote} is tool set that has very similar ambitions to \textit{gsmodutils}.
It features a fully specified set of tests, including custom test cases and has strong version control integration with git.
A core difference between these projects is that \textit{gsmodutils} has a stronger focus on reducing the redundancy in model storage through the use of \textit{design deltas}, as described above.
Similarly, a core goal of \textit{gsmodutils} is to allow easy import and export outside of the framework for compatibility with other modelling suites.
It should be noted that, as memote is written in python, utilises COBRApy and, at the time of writing, it is fully compatible with \textit{gsmodutils}.
\\
\textbf{Cameo:} \cite{cardoso2017cameo} is a set of strain design utilities, such as genetic algorithms for finding optimal gene knock-out
strategies, as well as other flux balance analysis utilities. Written in python and part of the COBRApy suite of applications,
gsmodutils integrates easily with cameo.
Indeed, making a set of design changes can easily be integrated into \textit{gsmodutils} through the python API.
\\
\textbf{Model repositories:} models are frequently shared, at the time of publication through services such as BiGG \cite{king2015bigg} and Biomodels \cite{chelliah2013biomodels}. 
Whilst these repositories encourage the reuse of models and the reproducibility of \textit{in silico} predictions they are not designed to improved collaboration.
The software presented here is designed with the notion that genome scale models are never finished, \textit{per se}, but under continuous development.
The cornerstone of this is the use of test cases, which formalise modelling validation criteria.

>>>>

\section{Related work}
\textbf{Memote:} \cite{lieven2017memote} is tool set that has very similar ambitions to \textit{gsmodutils}.
It features a fully specified set of tests, including custom test cases and has strong version control integration with git.
A core difference between these projects is that \textit{gsmodutils} has a stronger focus on reducing the redundancy in model storage through the use of \textit{design deltas}, as described above.
Similarly, a core goal of \textit{gsmodutils} is to allow easy import and export outside of the framework for compatibility with other modelling suites.
It should be noted that, as memote is written in python, utilises COBRApy and, at the time of writing, it is fully compatible with \textit{gsmodutils}.
\\
\textbf{Cameo:} \cite{cardoso2017cameo} is a set of strain design utilities, such as genetic algorithms for finding optimal gene knock-out
strategies, as well as other flux balance analysis utilities. Written in python and part of the COBRApy suite of applications,
gsmodutils integrates easily with cameo.
Indeed, making a set of design changes can easily be integrated into \textit{gsmodutils} through the python API.
\\
\textbf{Model repositories:} models are frequently shared, at the time of publication through services such as BiGG \cite{king2015bigg} and Biomodels \cite{chelliah2013biomodels}. 
Whilst these repositories encourage the reuse of models and the reproducibility of \textit{in silico} predictions they are not designed to improve collaboration.
The software presented here is designed with the notion that genome scale models are never finished, \textit{per se}, but under continuous development.
The cornerstone of this is the use of test cases, which formalise modelling validation criteria.
